A Java Wrapper For Embarrassingly Parallel Problems

### 2013-11-10 paper/paper.tex
Paper revision #2 completed

The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarrassingly parallel programs in the biological sciences. 
TALK ABOUT CLUSTERING
With several applications that 
would benefit from parallelism in this field, it was obvious it would be 
desirable to develop a framework for creating wrapper programs.

@@

\begin{thebibliography}{1}
\bibitem{history}
Moler, Cleve. "Matrix Computation on Distributed Memory Multiprocessors."
Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
T. Heath. Philadelphia: SIAM, 1986. N. pag. Print.
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., ``\emph{KaKs Calculator: 
calculating Ka and Ks through model selection and model averaging.},'',
Genomics Proteomics Bioinformatics, November 2006.
\end{thebibliography}

>>>>

The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarrassingly parallel programs in the biological sciences. To deal with large
amounts of data, the best method is often to group them into clusters. 
Hierarchical clustering algorthms take the data and then organize into
hierarchical structure, usually a dendrogram, based on a priority matric. There 
are hierarchical clustering algorithms that can be implemented in parallel using
an embarrassingly parallel approach.  With several applications that would 
benefit from parallelism in this field, it was obvious it would be desirable to 
develop a framework for creating wrapper programs. \cite{cluster}

@@

\begin{thebibliography}{1}
\bibitem{history}
Moler, Cleve. ``\emph{Matrix Computation on Distributed Memory Multiprocessors."
}, Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
T. Heath. Philadelphia: SIAM, 1986. N. pag. Print.
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{KaKs Calculator: 
calculating Ka and Ks through model selection and model averaging},
Genomics Proteomics Bioinformatics, November 2006.
\bibitem{cluster}
Rua, Xu, Wunsch, Donald II, \emph{Survey of Clustering Algorithms},
IEEE Transactions on Neural Networks VOL. 16, NO. 3, MAY 2005
\end{thebibliography}
